experDesign: helping performing experiments on collections

### 2021-04-14 README.Rmd

>>>>

 - The [Omixer](https://bioconductor.org/packages/Omixer/) package handles both 
numeric and categorical data (converting categorical variables to numeric). But both the same way either Pearson's Chi-squared Test if there are few samples or Kendall's correlation. It does allow to protect some spots from being used.
